---
title: "CSBG Agency Report"
output:
  word_document:
    reference_docx: word_template.docx
date: "Vintage 2023"

fontsize: 11pt
editor: visual


params:
    entity: entity
    rpt_title: rpt_title
    curYr : curYr
    fileLoc : fileLoc
---

```{r}
#| echo: false
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(accessr)
outputDir <- paste0(params$entity)

logo_str <- "./www/co_dola_off_sd_rgb_email.png"
logo_alt <- "State Demography Office Logo"

acsYr <- paste0(params$curYr - 4,"-",params$curYr)



```

```{r, fig.alt = logo_alt, echo = FALSE, out.width="50%", results='asis'}
knitr::include_graphics(logo_str)
```

The charts in this document compares *`r params$entity`* CSBG agency to National and State statistics from the

-   Vintage `r params$curYr` State Demography Office Population Estimates,
-   Unemployment data from the Bureau of Labor Statistics, and
-   The `r acsYr` American Community Survey 5-Year Data.

Data tables are available in the *`r params$entity` Data Tables* spreadsheet in the entity folder.

## County Map

```{r, echo = FALSE, fig.alt=params$fileLoc[1,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[1,1])
```

## Contents of the `r params$entity` folder

Data tables are available in the *`r params$entity` Data Tables* spreadsheet in the agency folder.

County-level charts are available in the sub-folders.

-   Contents of Sub folders
    -   *Age Distribution*: Age Pyramids by Sex
    -   *Unemployment Trend*: Two Year Unemployment Rate Trend Line
    -   *Poverty Levels*: Individuals by Household Income as a Percentage of the Federal Poverty Level
    -   *Education By Poverty*: Educational Attainment by Poverty Status, Age 25 and Older
    -   *Age by Poverty*: Age by Poverty Status
    -   *Disability by Poverty*: Disability Status by Age and Poverty Status
    -   *Families by Poverty*: Family Composition by Poverty Status
    -   *Housing Tenure by Poverty*: Housing Tenure by Family Composition and Poverty Status
    -   *SNAP Program by Poverty*: SNAP Program Participation by Poverty Status
    -   *Health Insurance by Poverty*: Health Insurance by Poverty Status

## Age Distribution

### United States

```{r, echo = FALSE, fig.alt=params$fileLoc[2,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[2,1])
```

### Colorado

```{r, echo = FALSE, fig.alt=params$fileLoc[3,2],out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[3,1])
```

\newpage

### `r params$entity`

```{r, echo = FALSE, fig.alt=params$fileLoc[4,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[4,1])
```

## Unemployment Rate

```{r echo = FALSE, fig.alt=params$fileLoc[5,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[5,1])
```

\newpage

## Poverty Levels

```{r, echo = FALSE, fig.alt=params$fileLoc[6,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[6,1])
```

## Educational Attainment by Poverty Status, Population Age 25 and Older

```{r, echo = FALSE, fig.alt=params$fileLoc[7,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[7,1])
```

\newpage

## Age by Poverty Status

```{r, echo = FALSE, fig.alt=params$fileLoc[8,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[8,1])
```

## Disability Status by Age and Poverty Status

```{r, echo = FALSE, fig.alt=params$fileLoc[9,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[9,1])
```

\newpage

## Family Composition by Poverty Status

```{r, echo = FALSE, fig.alt=params$fileLoc[10,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[10,1])
```

## Housing Tenure by Family Composition and Poverty Status

```{r, echo = FALSE, fig.alt=params$fileLoc[11,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[11,1])
```

\newpage

## SNAP Program Participation by Poverty Status

```{r, echo = FALSE, fig.alt=params$fileLoc[12,2],out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[12,1])
```

## Health Insurance by Poverty Status

```{r, echo = FALSE, fig.alt=params$fileLoc[13,2], out.widh="70%", results='asis'}
knitr::include_graphics(params$fileLoc[13,1])
```
